---
title: "RWorksheet_Almayo#3B"
author: "Josh Christian Almayo"
date: "2024-10-12"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
1.
```{r}
sex <- c(2, 2, 1, 2, 2, 2, 2, 2, 2, 2, 1, 2, 2, 2, 2, 2, 2, 2, 1, 2)
fathers_occupation <- c(1, 3, 3, 3, 1, 2, 3, 1, 1, 1, 3, 2, 1, 3, 3, 1, 3, 1, 2, 1)
persons_at_home <- c(5, 7, 3, 8, 5, 9, 6, 7, 8, 4, 7, 5, 4, 7, 8, 8, 3, 11, 7, 6)
siblings_at_school <- c(6, 4, 4, 1, 2, 1, 5, 3, 1, 2, 3, 2, 5, 5, 2, 1, 2, 5, 3, 2)
types_of_houses <-c(1, 2, 3, 1, 1, 3, 1, 2, 2, 3, 2, 3, 2, 2, 3, 3, 3, 3, 3, 2)

sex
fathers_occupation
persons_at_home
siblings_at_school
types_of_houses
```




```{r}
df <- data.frame( sex, fathers_occupation, persons_at_home, siblings_at_school, types_of_houses)

df
```

```{r}
mean_siblings <- mean(df$siblings_at_school)
mean_siblings

```
\\the mean number of siblings is 2.95

```{r}
first_two_rows <- df[1:2,]
first_two_rows

```

```{r}
extract_datas <- df[c(3, 5), c(2, 4)]
extract_datas
```

```{r}
types_of_houses <- (df$types_of_houses)
types_of_houses
```

```{r}
male_farmer_respondents <- df[(df$Sex == 1) & (df$Fathers_Occupation == 1), ]
male_farmer_respondents
```

2.
```{r}
df = data.frame(Ints=integer(),

Doubles=double(), Characters=character(),
Logicals=logical(),
Factors=factor(),
stringsAsFactors=FALSE)

print("Structure of the empty dataframe:")
print(str(df))
```
\\factros columns has 0 levels, indicating that no unique category in data.

3. 

```{r}
House_hold <- read.csv("/cloud/project/worksheet3/HouseholdData.csv")
House_hold
```

```{r}
df$sex <- factor(df$sex)
df$sex <- as.integer(df$sex)
sex
```

```{r}
df$types_of_houses <- factor(df$types_of_houses)
df4types_of_houses <- as.integer(df$types_of_houses)
types_of_houses
```

```{r}
df$fathers_occupation <- factor(df$fathers_occupation)
fathers_occupation
```
\\it shows number of fathers in a certain occupation.

```{r}
female_driver_respondents <- df[(df$Sex == 2) & (df$Fathers_Occupation == 3),]
female_driver_respondents
```
\\0 rows|1-7 of 9 columns

```{r}
respondents_have_5_or_more_siblings <- df [(df$siblings_at_school >= 5)]
respondents_have_5_or_more_siblings
```
4. 

\\The graph displays the quantity of tweets sent daily between July 14, 2020, and July 20, 2020, a span of seven days. The sentiment of the tweets is classified as either good, neutral, or negative. It shows that the sentiment is not consistent and varies from day to day.









