---
title: "RWorksheet_Almayo#4a"
author: "Josh Christian Almayo"
date: "2024-10-14"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
1.

\\The table below shows the data about shoe size and height. Create a data frame.
a. Describe the data

\\the data shoes the different measurement of height, and shoesize of the different genders.
```{r}

household_data <- data.frame(
shoesize =  c(6.5, 9.0, 8.5, 8.5, 10.5, 7.0, 9.5, 9.0, 13.0, 7.5, 10.5, 8.5, 12.0, 10.5, 13.0, 11.5, 8.5, 5.0, 10.0, 6.5, 7.5, 8.5, 10.5, 8.5, 10.5, 11.0, 9.0, 13.0),


height =  c(66.0, 68.0, 64.5, 65.0, 70.0, 64.0, 70.0, 71.0, 72.0, 64.0, 74.5, 67.0, 71.0, 71.0, 77.0, 72.0, 59.0, 62.0, 72.0, 66.0, 64.0, 67.0, 73.0, 69.0, 72.0, 70.0, 69.0, 70.0),



gender = c("F","F","F", "F", "M", "F", "F", "F", "M", "F", "M", "F", "M", "M", "M", "M", "F", "F", "M", "F", "F", "M", "M", "F", "M", "M", "M", "M")
)

```

B. 
Create a subset by males and females with their corresponding shoe size and height.
What its result? Show the R scripts.


```{r}
males <- subset(household_data, gender == "M" & shoesize&height)
females <- subset(household_data, gender == "F" & shoesize&height)
males
females
```





```{r}
meanA <- mean(household_data$shoesize)
meanB <- mean(household_data$height)
meanA
meanB
```

d. is there a relationship between shoe size and height? Why?

\\there is a relationship  between height and shoe size, taller individual tends to have larger shoe size because of body proportion.


3. Then check the summary() of the months_vector and factor_months_vector. | Inter-
pret the results of both vectors. Are they both equally useful in this case?

\\yes, since it shows the summary of levels of the months.
```{r}
months <- c("March","April","January","November","January",
"September","October","September","November","August",
"January","November","November","February","May","August", "July","December","August","August","September","November","February",
"April")
```
```{r}
months_vector <- c(months)
months_vector
```

```{r}
factor_months_vector <- factor(months)
factor_months_vector
```




```{r}
summary(months)

```
4.

```{r}
direction <- c("East", "West", "North")
frequency <- c(1,4,3)

direction
frequency

new_order_data <- factor(direction,levels = c("East","West","North"))
new_order_data
```
5.

a.
```{r}
import_march <- read.table("import_march.csv", header = TRUE, sep = "\t")
import_march
```
b.
```{r}
str(import_march)
```
\\it shows the structure of the imported csv file that has student, strat1,strat2 and strat3.







