---
title: "Rworksheet_Almayo#1"
author: "Josh Almayo"
date: "2024-09-23"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
age <- c(34, 28, 22, 36, 27, 18, 52, 39, 42, 29,
35, 31, 27, 22, 37, 34, 19, 20, 57, 49, 50, 37, 46, 25, 17, 37, 42, 53, 41,
51, 35, 24, 33, 41)
age
length(age)
```
\\there were 34 data points

```{r}
reciprocal_age <- 1/age

reciprocal_age
```


```{r}
new_age <- c(age,0,age)

new_age
```
\\there's an added age which is 0


```{r}
age <-c(34, 28, 22, 36, 27, 18, 52, 39, 42, 29,
35, 31, 27, 22, 37, 34, 19, 20, 57, 49, 50, 37, 46, 25, 17, 37, 42, 53, 41,
51, 35, 24, 33, 41)

sort(age)
```


```{r}
min_age <- min(age)
max_age <- max(age)

min(age)
max(age)
```


```{r}
data <- c(2.4, 2.8, 2.1, 2.5, 2.4, 2.2, 2.5, 2.3, 2.5, 2.3, 2.4, 2.7)
length(data)
data

Doubled_data <- data*2

Doubled_data
```
\\there were 12 data points
\\after writing the code doubled data, we can see that the inputs were doubled the value

```{r}
seq_1_to_100 <-1:100
```
```{r}
seq_20_to_60 <- 20:60
```
```{r}
mean_20_to_60 <- mean(seq_20_to_60)
```
```{r}
sum_51_to_91 <- sum(51:91)
```
\\there were 143 data points from 8.1 to 8.4
```{r}
seq_1_to_1000 <- 1:1000
```
\\a
```{r}
numdatapoints <- length(seq_1_to_100) +
length(seq_20_to_60) + 1 + 1

numdatapoints
```
\\b
```{r}
seq_1_to_100; seq_20_to_60;
mean_20_to_60; sum_51_to_91
```
\\c
```{r}
subset_data <-
seq_1_to_1000[seq_1_to_1000 <= 10]

max_value <- max(subset_data)

max_value
```
```{r}
not_divisible <- Filter(function(i) { all(i %% c(3, 5, 7) != 0) }, seq(100))

not_divisible
```
\\10
```{r}
seq_backwards <- seq(100, 1, by = -1)
```
\\11
```{r}
multiples_3_or_5 <- Filter(function(x) {x %% 3 == 0 || x %% 5 == 0}, seq(1, 24))

sum_multiples <- sum(multiples_3_or_5)
```
\\a
```{r}
num_data_points_10_11 <- length(seq_backwards) + length(multiples_3_or_5)
```
\\b
```{r}
seq_backwards; multiples_3_or_5; sum_multiples; num_data_points_10_11

```

\\12

\\output was error because x was assigned before assigned
value

\\13

```{r}
score <- c(72, 86, 92, 63, 88, 89, 91, 92, 75, 75, 77)

score[2]

score[3]
```
\\14
```{r}
a <- c(1, 2, NA, 4, NA, 6, 7)
print(a,na.print="-999")
```
\\NA becomes -999 when I put the code after the vector a

\\15
```{r}
name = readline(prompt="Input your name: ")

age = readline(prompt="Input your age: ")

print(paste("My name is",name, "and I am",age ,"years old."))

print(R.version.string)
```
\\code above has a personalize questions to user to input Datas, followed by R version string
